Integrating Social Visual Analysis and Deployment with RCloud

### 2015-03-27 relatedwork.tex
yes

\begin{figure}
\includegraphics[width=\linewidth]{fig/system/system.pdf}
\caption{\label{fig:system}A diagram of RCloud's architecture. Dashed
  lines represent features which not yet implemented. \carlos{Must remove anything that isn't implemented}}
\end{figure}

@@

\stephen{In addition to the immense foundation of work on systems
for statistical computing,}
There is much previous work that inspired or influenced ours.
Indeed, many studies have addressed requirements for future visual
analytics environments.
Previous work that we learned from includes:

@@

Our work has been inspired by and benefited from other efforts
to improve data analysis environments and processes,
including RStudio \cite{RStudio:2013:SWA},
the R packages Markdown \cite{Allaire:2014:MMR},
knitr \cite{Xie:2013:DDW}
and Shiny \cite{RStudio:2013:SWA},
and iPython notebooks \cite{Perez:2007:IAS}
to name a few. RStudio aims at providing an integrated development environment
for R, with support for publishing code in packages. Markdown,
knitR and Shiny augment R with sophisticated reporting capabilities, including
interactive web interfaces. IPython \cite{Perez:2007:IAS}
shares many of our goals, such as providing a comprehensive environment
for analysis and programming, and share-able documents on the web.
\stephen{Do we now need to introduce one of those remarks where we
explain that we are not the same as IPython.}

One overall goal is to reduce the gap between implementers and deployers
of technology in visual analytics. The fusion of development with production
operations in software release management (``DevOps'' \cite{Httermann:2012:DD}
or ``continuous integration'' \cite{Fowler:2006:Continuous}) is a trend in web
services and related fields.
By making it convenient for data scientists to expend just a little more effort
in the process of creating experiments, we may be able to eliminate the need
for programming teams to recreate their work in production, which has a high
penalty in time, expense and accuracy.

>>>>

\begin{figure*}
  \centering
\includegraphics[width=.75\linewidth]{fig/system/system.pdf}
\caption{\label{fig:system}A diagram of RCloud's architecture. }
\end{figure*}

@@

There is much previous work that inspired or influenced ours.
Indeed, many studies have addressed requirements for future visual
analytics environments.
Previous work that we learned from includes:

@@

\stephen{We have a problem we already went over some of this.}
Our work has been inspired by and benefited from other efforts
to improve data analysis environments and processes. Building in
the immense foundation of systems for statistical graphics,
recent work includes RStudio \cite{RStudio:2013:SWA},
the R packages Markdown \cite{Allaire:2014:MMR},
knitr \cite{Xie:2013:DDW}
and Shiny \cite{RStudio:2013:SWA},
and iPython notebooks \cite{Perez:2007:IAS}
to name a few. RStudio aims at providing an integrated development environment
for R, with support for publishing code in packages. Markdown,
knitR and Shiny augment R with sophisticated reporting capabilities, including
interactive web interfaces. IPython \cite{Perez:2007:IAS}
shares many of our goals, such as providing a comprehensive environment
for analysis and programming, and share-able documents on the web.
\stephen{Do we now need to introduce one of those remarks where we
explain that we are not the same as IPython.}

One overall goal is to reduce the gap between implementers and deployers
in visual analytics. The fusion of development with production
operations in software release management (``DevOps'' \cite{Httermann:2012:DD}
or ``continuous integration'' \cite{Fowler:2006:Continuous}) is a trend in web
services and related fields.
By making it convenient for data scientists to expend just a little more effort
when creating experiments, we may be able to eliminate the need for programming
teams to recreate their work to deploy it in production,
which has a high cost in time, expense and accuracy.
